Quality Definitions of Qualities

### 2021-10-04 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Minor update to unambiguous quality section

A specification is unambiguous when it has a unique interpretation.  If
there is a possibility that two readers will have two different
interpretations, than the specification is ambiguous.  \wss{When I get the
Ghezzi text back from Olu, I'll check to see if they have anything to add to
this definition.}

A Software Requirements Specification (SRS) is unambiguous if, and only if,
every requirement stated therein has only one interpretation \citep{IEEE1998}.

>>>>

\begin{defn}
 A Software Requirements Specification (SRS) is unambiguous if, and only if,
 every requirement stated therein has only one interpretation \citep{IEEE1998}.
\end{defn}
